Research Proposal

### 2021-10-07 Reports/JOURNAL - Confidence Regions/ResearchProposal.tex
Update ResearchProposal.tex

Although very expressive, the Normalized Shannon Entropy is not able to describe all possible underlying dynamics.
In particular, for intermediate values of $H$, there is a wide variety of situations worth characterizing.
To this aim, \citet{LopezRuiz1995} proposed using the disequilibrium  $Q$, a measure of how far $\bm h$ is from an equilibrium or noninformative distribution.
They employed the Euclidean distance between $\bm h$ and the uniform probability distribution function.

We opt for the Jensen-Shannon distance to the uniform distribution $\bm{u} = \big(\frac{1}{D!^2}, \dots, \frac{1}{D!^2}\big)$, as it is a measure of how similar the underlying dynamics is to a non-informative process.
It is calculated as:
\begin{equation}
	Q'(\bm{h}, \bm{u}) = \sum_{\ell=1}^{D!^2} \Big(h_\ell \log\frac{h_\ell}{u_\ell} +
	u_\ell \log\frac{u_\ell}{h_\ell}
	\Big).
\end{equation}
This quantity is also called ``disequilibrium.''
The normalized disequilibrium is $ Q=Q'/\max\{Q'\}$.

>>>>

Although very expressive, the Normalized Shannon Entropy is not able to describe all possible underlying dynamics.
In particular, for intermediate values of $H$, there is a wide variety of situations worth characterizing.
To this aim, \citet{LopezRuiz1995} proposed using the disequilibrium  $Q$, a measure of how far $\bm h$ is from an equilibrium or non-informative distribution.
They employed the Euclidean distance between $\bm h$ and the uniform probability distribution function.

We opt for the Jensen-Shannon distance to the uniform distribution $\bm{u} = \big(\frac{1}{D!}, \dots, \frac{1}{D!}\big)$, as it is a measure of how similar the underlying dynamics is to a non-informative process.
It is calculated as:
\begin{equation}
	Q'(\bm{h}, \bm{u}) = \sum_{\ell=1}^{D!} \Big(h_\ell \log\frac{h_\ell}{u_\ell} +
	u_\ell \log\frac{u_\ell}{h_\ell}
	\Big).
\end{equation}
This quantity is also called ``disequilibrium.''
The normalized disequilibrium is $ Q=Q'/\max\{Q'\}$.
